Backscatter Modulation Design for Symbiotic Radio Networks

### 2022-01-24 main.tex
:pencil: Add initial thresholding proof

			\begin{proof}
				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in definition, since otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$. Without loss of generality, we assume
				% $L \mid S$ and
				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{Note that the proof holds for general mapping and we focus on this case for the ease of notation.} The thresholding design problem can be expressed as
				\begin{maxi!}
					{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(c_{\mathcal{K}};z)}{\label{op:thresholding}}{\label{ob:backscatter_mutual_information}}
					\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
				\end{maxi!}

				Problem~\eqref{op:thresholding} is intricate due to the strict inequality constraint~\eqref{co:strict_inequality}. Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate the original constraints. The Lagrangian function for the relaxed problem is
				\begin{equation}
					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
				\end{equation}
				where $\mu_s$ is the Lagrange multiplier associated with the non-strict counterpart of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$. The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
				\begin{subequations}
					\begin{equation}
						- \nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^{\star} - \mu_s^{\star} = 0,
						\label{eq:stationarity}
					\end{equation}
					\begin{equation}
						\mu_s^{\star} \ge 0,
						\label{eq:dual_feasibility}
					\end{equation}
					\begin{equation}
						\mu_s^{\star} (t_{s-1}^{\star} - t_s^{\star}) = 0.
						\label{eq:complementary_slackness}
					\end{equation}
				\end{subequations}
				Since we require $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$. Therefore, \eqref{eq:stationarity} reduces to
				\begin{equation}
					\nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0.
				\end{equation}
			\end{proof}

>>>>

			\begin{proof}
				For any finite number of thresholds $S \in \mathbb{Z}_{++}$, let $\boldsymbol{t} \triangleq [t_0,\ldots,t_S]^T \in \mathbb{R}_{+}^{S \times 1}$ be the thresholding vector where $t_{s-1} < t_s$, $\forall s \in \mathcal{S} \triangleq \{1,\ldots,S\}$.\footnote{We consider strict inequality in the definition, as otherwise $S$ and $\boldsymbol{t}$ could be non-unique for a given thresholding scheme.} Denote the decision partition $s$ as $R_s \triangleq [t_{s-1},t_s)$. Without loss of generality, we assume
				% $L \mid S$ and
				$\mathcal{R}_j = \bigcup_{s \equiv j \pmod L} R_s$.\footnote{The proof holds for general mapping $R_s \mapsto \mathcal{R}_j$, and we focus on this specific case for the ease of notation.} The thresholding design problem can be expressed as
				\begin{maxi!}
					{\scriptstyle{\boldsymbol{t}}}{I_{\mathrm{B}}(c_{\mathcal{K}};z)}{\label{op:thresholding}}{\label{ob:backscatter_mutual_information}}
					\addConstraint{t_{s-1}}{< t_s,}{\quad \forall s \in \mathcal{S}.}{\label{co:strict_inequality}}
				\end{maxi!}

				Problem~\eqref{op:thresholding} is intricate due to the strict inequality constraint~\eqref{co:strict_inequality}. Following \cite{Nguyen2020}, we first relax it to the convex counterpart, then discard the solutions that violate the original constraints. The Lagrangian function for the relaxed problem is
				\begin{equation}
					L(\boldsymbol{t},\boldsymbol{\mu}) = - I_{\mathrm{B}}(c_{\mathcal{K}};z) + \sum_{s \in \mathcal{S}} \mu_s (t_{s-1} - t_s),
					% = \sum_{j \in \mathcal{L}} P(\bar{z}_j) \log P(\bar{z}_j) - \sum_{i \in \mathcal{L}} \sum_{j \in \mathcal{L}}
				\end{equation}
				where $\mu_s$ is the Lagrange multiplier associated with the non-strict version of \eqref{co:strict_inequality} and $\boldsymbol{\mu} \triangleq [\mu_1,\ldots,\mu_S]^T \in \mathbb{R}^{S \times 1}$. The corresponding \gls{kkt} conditions on the optimal primal and dual solutions are, $\forall s \in \mathcal{S}$,
				\begin{subequations}
					\begin{equation}
						- \nabla_{t_s^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) + \mu_{s-1}^{\star} - \mu_s^{\star} = 0,
						\label{eq:stationarity}
					\end{equation}
					\begin{equation}
						\mu_s^{\star} \ge 0,
						\label{eq:dual_feasibility}
					\end{equation}
					\begin{equation}
						\mu_s^{\star} (t_{s-1}^{\star} - t_s^{\star}) = 0.
						\label{eq:complementary_slackness}
					\end{equation}
					\label{eq:kkt_thresholding}
				\end{subequations}
				For \gls{dmtc} based on energy detection~\eqref{eq:energy_distribution}, it is trivial to conclude $t_0^{\star} = 0$ and $t_S^{\star} = \infty$. Besides, since $t_{s-1} < t_s$ by definition, \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} imply $\mu_s^{\star} = 0$, $\forall s \in \mathcal{S}$. As such, $\forall s' \in \mathcal{S} \setminus \{S\}$, \eqref{eq:kkt_thresholding} reduces to
				\begin{equation}
					\nabla_{t_{s'}^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z) = 0,
				\end{equation}
				which can be explicitly written as
				\begin{equation}
					\sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l) = 0,
					\label{eq:kkt_thresholding_explicit}
				\end{equation}
				where $j \equiv s \pmod L$. We notice that for a given $j$, $a_l \triangleq P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)}$ is a constant for all $s \equiv j \pmod L$. Plugging~\eqref{eq:energy_distribution} into \eqref{eq:kkt_thresholding_explicit}, we have
				\begin{equation}
					\sum_l a_l e^{-{h_s}/{\sigma_l^2}} = 0,
					\label{eq:optimal_thresholding_condition}
				\end{equation}
				which by Rolle's theorem has at most $L-1$ distinct real roots if $\sigma_i^2 \ne \sigma_j^2$, $i,j \in \mathcal{L}$.
				% where the directional derivative can be explicitly written as
				% \begin{subequations}
				% 	\begin{align}
				% 		\nabla_{t_{s'}^{\star}} I^{\star}_{\mathrm{B}}(c_{\mathcal{K}};z)
				% 		& = \sum_l P(x_l) \log \frac{P(z_j)}{P(z_{j+1})} \frac{P(z_{j+1} \mid x_l)}{P(z_j \mid x_l)} f(h_s \mid x_l)\\
				% 		& = 1
				% 	\end{align}
				% \end{subequations}
			\end{proof}
